Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and it's audio-description

### 2020-05-12 paper/main.tex
add figure to manuscript

>>>>

\todo[inline]{in der Abbildung der Regressoren-Korrelationen sind jetzt alle
    Regressoren drin; imo könnte man ein paar herausnehmen (die zur Kontrolle
    benutzen Filmschnitt-Regressoren in der AO-Analyse, die zur Kontrolle
    benutzen Descriptive-Nouns Regressoren (namentlich se\_new und se\_old), und ggf. [ein paar der] low-level features nuissance regressors.}

\begin{figure*} \centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table
        \ref{tab:av-events}). Regressors were convolved with FSL's
        ``Double-Gamma HRF'' as a model of the hemodynamic response function,
        temporally filtered with the same high-pass filter (cut-off
        \unit[150]{s}) as the BOLD time series, and concatenated across runs
    before performing the correlation.}
    \label{fig:reg-corr}
\end{figure*}
